Parallelization of Fast $\ell_1$-Minimization for Face Recognition

### 2011-03-23 main.tex
Fixed missing \end{document}
Updated figure

\subsection{GPU Implementation}
\label{sec:alignment_implementation_gpu}

This section discusses how to implement algorithm
\eqref{alg:iterative_alignment} on the GPU.  Like for the CPU case, many GPU
implementation strategies were explored during the course of our development,
and are only mentioned briefly.  Listed in order of increasing performance
based on a synthetic benchmark of the $\ell_1$ minimization step, they
included:
\begin{enumerate}
\item Solving a single problem instance at a time using Cublas\footnote{Nvidia provided BLAS implementation} (302 ms)
\item Pure CUDA C implementation solving one problem per SMP using cuda streams\footnote{Streams is a CUDA feature that allows multiple
kernels to be run concurrently} (70 ms)
\item Pure CUDA C implementation solving one problem per SMP using one large kernel call (36 ms)
\end{enumerate}

@@

Our proposed GPU implementation for the iterative alignment stage consists of a
single kernel that performs all of the test image alignment problems.  Each of
instance of the alignment problem is assigned its own thread block, and the GPU
hardware schedules as many of these thread blocks to run concurrently as the 
hardware will allow.

\begin{figure}
\centering
\includegraphics[width=3.4in]{figures/alignment_mapping_gpu}
\caption{Proposed mapping of alignment parallelism onto gpu concurrency}
\label{fig:alignment_mapping_gpu}
\end{figure}

The full resolution test image, along with its numerical derivatives in both
image directions, are stored in GPU texture memory. This  allows the
recomputation of $b(\tau)$ and $J(\tau)$, which essentially consist of warped
versions of the test image and its derivatives, to exploit the GPU's special
purpose hardware for bilinear interpolation.

@@

\subsection{CPU Implementation} Our CPU implementation of Algorithm
\ref{alg:alm_rec} was written in C++.  For operations in the algorithm that map
nicely onto the BLAS API (such as SGEMV, SAXPY {\bf? Victor, fill in here}), we
call Intel's MKL BLAS library, which internally takes advantage of the SSE
units on all available CPU cores. 
{\bf TODO: Our current implementation links against the MKL
library provided internally with matlab; we are in the process of updating the code to link directly against a newer version
of MKL}

@@

>>>>

\subsection{GPU Implementation}
\label{sec:alignment_implementation_gpu}
This section discusses how to efficently map the two levels of parallelism
available in iterative face alignment to the two levels of concurrency
available in the NVIDIA Fermi GPU architecture.

Our proposed GPU implementation for the iterative alignment stage consists of a
single kernel that performs all of the test image alignment problems.  Each of
instance of the alignment problem is assigned its own thread block, and the GPU
hardware schedules as many of these thread blocks to run concurrently as the 
hardware will allow.  
This mapping of the alignment problem onto the concurrency provided by the pair
of CPUs is visualized in Figure \ref{fig:alignment_mapping_gpu}.
\begin{figure}
\centering
\includegraphics[width=3.4in]{figures/alignment_mapping_gpu}
\caption{Proposed mapping of alignment parallelism onto gpu concurrency}
\label{fig:alignment_mapping_gpu}
\end{figure}
The full resolution test image, along with its numerical derivatives in both
image directions, are stored in GPU texture memory. This  allows the
recomputation of $b(\tau)$ and $J(\tau)$, which essentially consist of warped
versions of the test image and its derivatives, to exploit the GPU's special
purpose hardware for bilinear interpolation.

\subsection{Other Implementation Strategies}
Several GPU implementation strategies were explored during the course of our
development, and are only mentioned briefly.  Listed in order of increasing
performance based on a synthetic benchmark of the $\ell_1$ minimization step,
they included:
\begin{enumerate}
\item Solving a single problem instance at a time using Cublas\footnote{Nvidia provided BLAS implementation} (302 ms)
\item Pure CUDA C implementation solving one problem per SMP using cuda streams\footnote{Streams is a CUDA feature that allows multiple
kernels to be run concurrently} (70 ms)
\item Pure CUDA C implementation solving one problem per SMP using one large kernel call (36 ms)
\end{enumerate}

@@

@@

\subsection{CPU Implementation} Our CPU implementation of Algorithm
\ref{alg:alm_rec} was written in C++.  For operations in the algorithm that map
nicely onto the BLAS API (such as SGEMV, SAXPY {\bf? Victor, fill in here}), we
call Intel's MKL BLAS library, which internally takes advantage of the SSE
units on all available CPU cores.

@@

\end{document}
